Detecting Facial Expressions in Professional Tennis Matches

### 2017-07-28 Report06-12.Rmd
Added colour scheme

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "13 February 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

@@

    #read in image
    image <- readImage(paste0("figures/", i))
    #used in analyses
    #image <- readImage(paste0("images/", i))

@@

  }
  if(matchBox){
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=FaceKey, group=FaceID), fill=NA) +
      guides(colour = "none")
  }
  else{
    group.colors <- c(Animetrics = "#B3E2CD",
                      Google = "#FDCDAC",
                      Manual = "#CBD5E8",
                      Microsoft = "#F4CAE4",
                      Skybiometry = "#E6F5C9")

    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=type, group=FaceID), fill=NA) +
      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") + 
      coord_fixed(ratio=0.85) + scale_colour_manual(values=group.colors)
    }

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +
    ylab("Proportion of faces matched") + xlab(factorVar)
}

@@

```{r PotentialFaceData, fig.cap = "\\label{fig:PotentialFaceData}  Potential Face Boxes Per API: The bar chart shows the number of Potential Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more potential faces than the next best API, Microsoft."}
ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
  geom_bar(position="dodge") +
  xlab("Facial Recognition APIs") +
  scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
  ylab("Number of Potential Faces") + 
  guides(fill=FALSE) +
  labs(caption="")
```

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "28 July 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

# colour scheme
type.colours <- c(Animetrics = "#B3E2CD",
                      Google = "#FDCDAC",
                      Manual = "#CBD5E8",
                      Microsoft = "#F4CAE4",
                      Skybiometry = "#E6F5C9")

@@

    #read in image
    #image <- readImage(paste0("figures/", i))
    #used in analyses
    image <- readImage(paste0("images/", i))

@@

  }
  if(matchBox){
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=FaceKey, group=FaceID), fill=NA) +
      guides(colour = "none")
  }
  else{
    p1 <- p + geom_rect(data=faceData, 
                        aes(xmin=minX, ymin=-maxY, xmax=maxX, ymax=-minY, 
                            color=type, group=FaceID), fill=NA) +
      guides(colour = guide_legend(""))  + theme(legend.position = "bottom") +
      coord_fixed(ratio=0.85) + scale_color_manual(type.colours)
    }

@@

# Create graphs of factors in manual proportions
getManualCount <- function(type, count) {
  return(count[type == "Manual"])
}
ggplotProportion <- function(dataset, factorVar){
  factorVar <- deparse(substitute(factorVar))
  dataset <- dataset %>% filter(matchesManual) %>% group_by_(factorVar, "type") %>% summarise(nTotal=n()) %>% group_by_(factorVar) %>% mutate(ManualCount = getManualCount(type, nTotal)) %>%
    mutate(proportion = nTotal/ManualCount) %>% rename_(xvar = factorVar) %>% filter(type!="Manual")
   ggplot(dataset, aes(x=xvar, y=proportion, group = reorder(type, -proportion), fill=type)) + geom_bar(stat = "identity", position = "dodge") +  ylab("Proportion of faces matched") + xlab(factorVar) + scale_colour_manual(values=type.colours)
}

@@

```{r PotentialFaceData, fig.cap = "\\label{fig:PotentialFaceData}  Potential Face Boxes Per API: The bar chart shows the number of Potential Face Boxes produced by each API, comparing the height of the bars indicates that Google's Facial Recognition API recognized almost 1000 more potential faces than the next best API, Microsoft."}
ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + 
  geom_bar(position="dodge") +
  xlab("Facial Recognition APIs") +
  scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +
  ylab("Number of Potential Faces") + 
  guides(fill=FALSE) +
  labs(caption="") + scale_fill_manual(values=type.colours)
```
